### 2024-09-24 sections/projects.tex
Create projects.tex

%% DEPRECATED

\cvsection{Funding \& Research Projects}

@@

\begin{cvhonors}
\cvhonor
{Chilean Political Science Impact Ranking} 
{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
{Coordinator}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{COVID-19 Pandemic in South America}
{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
{Coordinator}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Gender Turnout and Elected Representatives in Iceland Municipal Elections}
{Prof. Petra Schleiter, Department of Politics and International Relations and St Hilda's College, University of Oxford}
{Research Assistant}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Survival of the Senior Civil Servants in the Chilean Executive Branch}
{Funded by the Universidad de Santiago de Chile (Academic Performance Agreement). {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/WBF6M}{10.17605/OSF.IO/WBF6M}}
{Researcher}
{2018}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Political System and Visibility of Actors in the Public Debate Articulated by the Elite Press, 1990-2018}
{Funded by the Universidad Alberto Hurtado (XVI Promotion of Research Fund, Ximena Orchard, Principal Investigator)}
{Researcher}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Transparency and Publication Dynamics on the Latin American Public Administration}
{Funded by the Universidad de Santiago (USA1498.57, Diego Barría, Principal Investigator)}
{Researcher}
{2017}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Public Service Motivation, Open Government and Preferences on Public Services}
{Funded by the Universidad de Santiago (USA1498.37, Diego Barría, Principal Investigator)}
{Researcher}
{2016}
\end{cvhonors}

%% PENDING PROJECTS

>>>>

\cvsection{Relevant Research Projects}

@@

\begin{cvhonors}
\cvhonor
{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about {\pounds} 800 000. Period: 2024-2026.}
{Dutch Research Agency}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about {\pounds} 1 500. Period: 2024-2025.}
{UDP}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
{OpenAI Academic Programme, Principal Investigator, about {\pounds} 5 000. Period: 2024.}
{OpenAI}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Unravelling the Rule of Law: A Machine Learning Approach}
{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about {\pounds} 45 000. Period: 2023-2024.}
{Dutch Research Agency}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about {\pounds} 1 700. Period: 2022.}
{USACH}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Resarch Associate (Ximena Orchard, Principal Investigator), about {\pounds} 3 000. Period: 2019.}
{UAH}
{2019}
\end{cvhonors}

@@
